---
title: "Data-Rep-Project"
author: "NICK"
date: "2024-04-06"
output: html_document
---

# Hello Tony! Welcome to my data replication project
## Today, I will be replicating some figures from the nature article:
# Social trauma engages lateral septum circuitry to occlude social reward
## Before we began, it's important for me to be honest...
## Most neuroscienist or pharmacologist do not give out well made data.frames for R, in fact, the ones from this paper gave the data for all figure parts on an excel sheet and color coordinated them
## This is not ideal for data wrangling, so I manually remade the excel sheet so it would be readable for R, I wanted to address that first and I'll show you why I do so in the prelude below

### Also, since it is just numbers in excel I am not able to determine if the data.frame I am building has the same values for the same animals, like between figure 1b and 1c, therefore, I will not be doing Figure 1e + f + j + k, the way the data is just doesn't give me a good grasp of the data groups

```{r}
library(tidyverse)
library(skimr)
#future Nick here, I tried to bring in the excel sheet, and it looked hideus...
# It looks amazing for lazy neuro data analysis but is a nightmare for this
# so this is my modified version:
d <- read.csv("https://raw.githubusercontent.com/nickmrussell/Russell-Data-Analysis-Replication/master/fig_1.csv")

head(d)
skim(d)
```

# Figure 1b, c, & d
## Showing a decrease in social activity after female mice experience long-term social stress in the form of social defeat
![alt text here](path-to-image-here)
```{r}
# Filtering the data for only the ladies
f <- d %>% filter(sex == "F")
# Figure 1b, social interaction ratio by group via one-way ANOVA
a1 <- aov(data = f, SI.Ratio ~ as.factor(Treatment))
summary(a1)
# Followed by a Tukey multiple-comparisions test
TukeyHSD(a1)
se1 <- sd(f$SI.Ratio)/sqrt(count(f))

g <- ggplot(f, aes(x = SI.Ratio, y = as.factor(Treatment), fill = as.factor(Treatment)))
g <- g +  geom_bar(stat = "summary", show.legend = FALSE) 
g <- g + scale_fill_manual(values = c("darkgrey", "red", "lightgrey")) 
g <- g + theme_classic() + geom_point() + xlim(0, 2.5) + theme(axis.title.y=element_blank(), legend.position = "none")
print(g)

```
![an image caption Source:fig_1b](data_rep/fig_1b)

## There seems to be more spread in the figure 1b graph than in the publication, I am unsure as to why, it could be due to the differences in how I set my x axis max or just aesthetic choices



```{r}
# Fig. 1c: amount of time in seconds spent socially investigating
a2 <- aov(data = f, Social_Investigation ~ as.factor(Treatment))
summary(a2)
# Followed by a Tukey multiple-comparisions test
TukeyHSD(a2)
se2 <- sd(f$Social_Investigation)/sqrt(count(f))

g <- ggplot(f, aes(x = as.factor(Treatment), y = Social_Investigation, fill = as.factor(Treatment)))
g <- g +  geom_bar(stat = "summary", show.legend = FALSE) 
g <- g + scale_fill_manual(values = c("lightgrey", "red", "darkgrey")) 
g <- g + theme_classic() +  geom_point() + theme(axis.title.x=element_blank(), legend.position = "none") + labs( y = "Social Investigation (s)") + ylim(0, 200) + scale_y_continuous(expand = c(0,0), limits = c(0,200))
print(g)

```

```{r}
# Fig. 1d: still female data, but its the count of times the mouse socially avoided the novel mouse
a3 <- aov(data = f, Social_Avoidance ~ as.factor(Treatment))
summary(a3)
# Followed by a Tukey multiple-comparisions test
TukeyHSD(a3)
g <- ggplot(f, aes(x = as.factor(Treatment), y = Social_Avoidance, fill = as.factor(Treatment)))
g <- g +  geom_bar(stat = "summary", show.legend = FALSE) 
g <- g + scale_fill_manual(values = c("lightgrey", "red", "darkgrey")) 
g <- g + theme_classic() +  geom_point() + theme(axis.title.x=element_blank(), legend.position = "none") + labs( y = "Social Avoidance (count)") + ylim(0, 10) + scale_y_continuous(expand = c(0,0), limits = c(0,10))
print(g)
```


# Figure 1g, h, & i
## Time for the male mice!
```{r}
# Filtering for the fellas
m <- d %>% filter(sex == "M")
# Figure 1b, social interaction ratio by group via one-way ANOVA
a4 <- aov(data = m, SI.Ratio ~ as.factor(Treatment))
summary(a4)

# Followed by a Tukey multiple-comparisions test
TukeyHSD(a4)

g <- ggplot(m, aes(x = SI.Ratio, y = as.factor(Treatment), fill = as.factor(Treatment)))
g <- g +  geom_bar(stat = "summary") 
g <- g + scale_fill_manual(values = c("darkgrey", "red", "lightgrey")) 
g <- g + theme_classic() +  geom_point() + xlim(0, 4) + theme(axis.title.y=element_blank(), legend.position = "none")
print(g)

```

```{r}
# Fig. 1c: amount of time in seconds spent socially investigating
a5 <- aov(data = m, Social_Investigation ~ as.factor(Treatment))
summary(a5)
# Followed by a Tukey multiple-comparisions test
TukeyHSD(a5)

g <- ggplot(m, aes(x = as.factor(Treatment), y = Social_Investigation, fill = as.factor(Treatment)))
g <- g +  geom_bar(stat = "summary") 
g <- g + scale_fill_manual(values = c("lightgrey", "red", "darkgrey")) 
g <- g + theme_classic() +  geom_point() + theme(axis.title.x=element_blank(), legend.position = "none") + labs( y = "Social Investigation (s)") + ylim(0, 300) + scale_y_continuous(expand = c(0,0), limits = c(0,300))
print(g)
```
```{r}
# Fig. 1d: count of times the mouse socially avoided the novel mouse
a6 <- aov(data = m, Social_Avoidance ~ as.factor(Treatment))
summary(a6)
# Followed by a Tukey multiple-comparisions test
TukeyHSD(a6)
g <- ggplot(m, aes(x = as.factor(Treatment), y = Social_Avoidance, fill = as.factor(Treatment)))
g <- g +  geom_bar(stat = "summary") 
g <- g + scale_fill_manual(values = c("lightgrey", "red", "darkgrey")) 
g <- g + theme_classic() +  geom_point() + theme(axis.title.x=element_blank(), legend.position = "none") + labs( y = "Social Avoidance (count)") + ylim(0, 40) + scale_y_continuous(expand = c(0,0), limits = c(0,40))
print(g)
```



## Hopefully you found that interesting because most of the field just does ANOVAs and t-tests, I was orignally planning on running some of the linear regressions and two-way ANOVAs in this paper, but this week has been hectic, here is what I currently happenening as I write this:
### -My Experiments have started a couple weeks ago and I am working everyday until I fly home in late May
### -I have two poster presentations, one the day after this was originally due and another Monday
### -I am neck deep in grant writing
### -My cat is currently undergoing exams for surgery for Friday
### While there are better ways for me to manage everything and reach out, I have been swamped and I have at least done above the bare minimum. I
